---
title: "STA 210 Histogram"
author: "Parker Williams"
date: "2023-10-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Frequency table
```{r}
load("aflsmall.rdata")
table(afl.margins)
```

## Histogram for numeric
```{r}
hist(afl.margins)
hist(afl.margins, labels = T)
```

```{r}
# (a) baseline
hist(afl.margins)
# (b) breaks = bins
hist(afl.margins, breaks = 5)
# (c) breaks = 0:116 (sequence)
hist(afl.margins, breaks = 0:116)
# (d) labels = number on top
hist(afl.margins, labels = T)
```

### How do we calculate bins number?
1. Sturge's rule
 $$ 1 + ceil(\log_2(n))$$
```{r}
1 + ceiling(log2(length(afl.margins)))
```

2. Freedman-Diaconis Rule

$$bin \, width \frac{2IQR}{n^{1/3}}$$


```{r}
library(psych)
width = 2*IQR(afl.margins)/176^(1/3)
width
```

$$bins = ceil \left(\frac{max - min}{width} \right) $$

```{r}
ceiling( (max(afl.margins)-min(afl.margins))/width )
```

### Final product of histogram
```{r}
hist(afl.margins, main = "2010 AFL margins", 
     xlab = "Margins",
      density = 20,
      border = "pink",
     col = "orange",
     labels = T,
     ylim = c(0, 40))
```

library(sportyR)
# MLB field
geom_baseball("mlb", display_range = "infield)

# library
library(ggplot2)
library(dplyr)
library(hrbrthemes)

# Build dataset with different distributions
data <- data.frame(
  type = c( rep("variable 1", 1000), rep("variable 2", 1000) ),
  value = c( rnorm(1000), rnorm(1000, mean=4) )
)

# Represent it
p <- data %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")
    




