---
title: 'Homework #6'
author: "Parker Williams"
date: "2023-10-16"
output:
  pdf_document: default
  pdf: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset
```{r}
library(ggplot2)
data(msleep)
head(msleep, 2)
tail(msleep, 2)
```

1. Histogram

Frequency Table
```{r}
min = min(msleep$sleep_total)
max = max(msleep$sleep_total)
tbl = table(cut(msleep$sleep_total, seq(1.9, 19.9, 4)))
as.data.frame(tbl)
```

(i) Hand-written Histogram

(ii) Histogram with R - 20 bins, labelled, shading lines (10 per inch)
```{r}
hist(msleep$sleep_total)
```

(iii) Calculation: Bins
- Sturge's Rule
```{r}
strgbins = ceiling(log2(length(msleep$sleep_total)) + 1)
strgbins
```

- Freedman's Rule
```{r}
iqr <- IQR(msleep$sleep_total)
n <- length(msleep$sleep_total)
fd_bins <- ceiling((2 * iqr) / (n^(1/3)))
fd_bins
```

(iv) The numbers of bins: 2 bins, 20 bins, 200 bins
```{r}
hist(msleep$sleep_total, breaks = 2, col = "blue", 
     main = "2 Bins")
hist(msleep$sleep_total, breaks = 20, col = "blue",
     main = "20 Bins")
hist(msleep$sleep_total, breaks = 200, col = "blue", 
     main = "200 Bins")
```

(v) Fix the errors
```{r}
hist(msleep$sleep_total, breaks = 20, col = "blue", 
     main = "Histogram of sleeping time",
     xlab = "Total time asleep per day (h)", ylab = "Count")
```

2. Boxplots

(i) boxplot
```{r}
boxplot(msleep$sleep_total, 
        main = "Title",
        ylab = "time")
```

(ii) coloring
```{r}
boxplot(msleep$sleep_total,
        main = "title",
        ylab = "time",
        whiskcol = "blue",
        boxcol = "red",
        col = "orange")
```

(iii) factor variable
```{r}
class(msleep$vore)
class(as.factor(msleep$vore))
levels(as.factor(msleep$vore))
```

boxplot
```{r}
boxplot(msleep$sleep_total ~ msleep$vore,
        main = "Boxplot of sleeping time by diets")
```

(iv)

- central value = median
- variability = IQR box
- skewness = shifted to the ?

3. Resume wordcloud graph
```{r}
library(wordcloud2)
myword = data.frame(word = c("statistical analysis", "math", "coding",
"visuals", "storytelling", "teamwork", "singing"),
                    rate = c(25, 20, 10, 10, 10, 5, 5))
# wordcloud2(myword, size = 0.5)
```






