---
title: "STA210 - Homework 5"
author: "Parker Williams"
date: "2023-10-09"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(worldfootballR)
prem_shooting_data = fb_season_team_stats(
  country = "ENG",
  gender = "M",
  tier = "1st",
  season_end_year = 2023,
  stat_type = "shooting")
```

Slice the data
```{r}
library(dplyr)
prem_shooting_data = prem_shooting_data%>%
  select(Squad, Gls_Standard, Dist_Standard, xG_Expected)
```

1. Cov(xG_Expected, Gls_Standard)
```{r}
cov(prem_shooting_data$xG_Expected, prem_shooting_data$Gls_Standard)
```

2. Interpret 1.
Covariance: It is a positive covariance that is approx 60% higher than expected and it trends right.

3. Cor(xG_Expected, Gls_Standard)
```{r}
cor(prem_shooting_data$xG_Expected, prem_shooting_data$Gls_Standard)
```

4. Correlation: It has a strong positive correlation, which means the expected amount of goals is almost perfectly correlated to the actual amount of goals.

5. Correlation matrix

-Cor(Gls_Standard, Dist_Standard)
```{r}
cor(prem_shooting_data$Gls_Standard, prem_shooting_data$Dist_Standard)
```

Meaning: This is a mild Negative correlation which means the distance doesnt really impact the actual amount of goals made

-Cor(xG_Expected, Dist_Standard)
```{r}
cor(prem_shooting_data$xG_Expected, prem_shooting_data$Dist_Standard)
```

Meaning: This is a mild Negative correlation which means the distance doesnt really impact the actual amount of goals made

What I can conclude about the most significant factor on gls_standard?
The most significant factor in gls_standard is the expected amount of goals and the actual amount of goals

## Extra Work
```{r}
library(corrplot)
G = cor(prem_shooting_data[ , -1])
corrplot(G, method = "number")
```
