---
title: "STA210 - Homework #9"
subtitle: "Data Merge"
author: "Parker Williams"
date: "2023-11-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section A. merge(df1, df2, by = "key_variable")

1. combine 'building' and 'data'
```{r}
buildings <- data.frame(location=c(1, 2, 3),
                      name=c("building1", "building2", 
                      "building3"))

data <- data.frame(survey=c(1,1,1,2,2,2),
                  location=c(1,2,3,2,3,1), 
                  efficiency=c(51,64,70,71,80,58))

buildingStats = merge(buildings, data, by = "location")

head(buildingStats, 5)
```


2. combine using separate keys
```{r}
buildings1 <- data.frame(location=c(1, 2, 3),
                        name=c("building1", "building2", 
                               "building3"))
data1 <- data.frame(survey=c(1,1,1,2,2,2),
                            LocationID=c(1,2,3,2,3,1),
                            efficiency=c(51,64,70,71,80,58))

buildingStats1 = merge(buildings1, data1, 
                       by.x = "location",
                       by.y = "LocationID")

head(buildingStats1, 5)
```

3. Outer join
```{r}
buildings <- data.frame(location=c(1, 2, 3),
                      name=c("building1", "building2", 
                      "building3"))

data <- data.frame(survey=c(1,1,1,2,2,2),
                  location=c(1,2,3,2,3,1), 
                  efficiency=c(51,64,70,71,80,58))

buildingStats2 = merge(buildings, data, all = T)

head(buildingStats2, 5)
```

4. Left join
```{r}
buildings <- data.frame(location=c(1, 2, 3),
                      name=c("building1", "building2", 
                      "building3"))

data <- data.frame(survey=c(1,1,1,2,2,2),
                  location=c(1,2,3,2,3,1), 
                  efficiency=c(51,64,70,71,80,58))

buildingStats3 = merge(buildings, data, all.x = T)

head(buildingStats3, 5)
```

5. Right join
```{r}
buildings <- data.frame(location=c(1, 2, 3),
                      name=c("building1", "building2", 
                      "building3"))

data <- data.frame(survey=c(1,1,1,2,2,2),
                  location=c(1,2,3,2,3,1), 
                  efficiency=c(51,64,70,71,80,58))

buildingStats4 = merge(buildings, data, by = NULL)

head(buildingStats4, 5)
```

6. Cross join
```{r}
buildings <- data.frame(location=c(1, 2, 3),
                      name=c("building1", "building2", 
                      "building3"))

data <- data.frame(survey=c(1,1,1,2,2,2),
                  location=c(1,2,3,2,3,1), 
                  efficiency=c(51,64,70,71,80,58))

buildingStats2 = merge(buildings, data, all = T)

head(buildingStats2, 5)
```

## Section B. Data merge using dplyr

Import data from Lahman library
```{r}
library(Lahman)
data("HallOfFame")
data("People")
names(HallOfFame)
print("--------------------")
names(People)
```

7. inner join
```{r}
library(dplyr)
df = inner_join(HallOfFame, People, by="playerID")
df = HallOfFame %>% inner_join(People, by = "playerID")
```

8. subset
```{r}
df1 = subset(df,
       subset = (yearID >= 2010),
       select = c("playerID", "height", "weight"))

df1 = df %>% filter(yearID >= 2010) %>%
  select(playerID, nameGiven, height, weight)
```

9. boxplot of height -> # of outliers??
```{r}
boxplot(df1$height, main = "Boxplot of Height", ylab = "Height")
```

10. cor(height, weight)
```{r}
cor(df1$height, df1$weight, use = "complete.obs")
```

There is evidence of a positive relationship between height and weight in the Hall of Fame data set, but the correlation is not extremely strong.











