---
title: "STA210 - Homework #8"
author: "Parker Williams"
date: "2023-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section A

Data import
```{r}
library(Lahman)
data("Batting")
summary(Batting$yearID)
```

1. Filter the data for the year 2021 for Dodgers (LAN) and Guardians (CLE)
```{r}
# Year 2021
condition = Batting$yearID == 2021
Batting21 = subset(Batting, subset = condition)

condition2 = Batting$teamID %in% c("LAN", "CLE")

LAN_CLE_21 = subset(Batting,
                    subset = condition & condition2)

# verification
levels(LAN_CLE_21$teamID)
LAN_CLE_21$teamID = droplevels(LAN_CLE_21$teamID)
levels(LAN_CLE_21$teamID)
```

2. Variable creation 
```{r}
LAN_CLE_21$enough.play = ifelse(LAN_CLE_21$G >= mean(LAN_CLE_21$G), "yes", "no")
```

3. Slicing
```{r}
df = subset(LAN_CLE_21, select = c(teamID, G, AB, HR, enough.play))
```

4. Tabulation

(a) cross-frequency table
```{r}
table(df$enough.play, df$teamID)
```

(b) marginal proportional table
```{r}
prop.table(table(df$enough.play, df$teamID), margin = 1)
```

(c) teamID vs HR
```{r}
table(df$HR, df$teamID)
```
In the context of player participation and home runs, LAN (Dodgers) has more players with 0 home runs and fewer players hitting more home runs, while CLE (Guardians) has a broader distribution of home run counts with more players hitting multiple home runs. This suggests potential differences in the power hitting abilities of the two teams.

## Section B

```{r}
age <- c(31, 49, 47, 38, 67, 52, 55)
salary <- c(103200, 106200, 150200, 10606, 10390, 14070, 10220)
gender <- c("male", "male", "male", "female", "female", "female", "male")
employee <- data.frame(age, salary, gender)
```

5. variable creation
```{r}
employee$f.age = cut(employee$age,
                     breaks = 3,
                     labels = c("Young", "Medium", "Aged")
                     )
employee$f.age = as.factor(employee$f.age)
```

6. variable creation
```{r}
library(lsr)
employee$sal = quantileCut(employee$salary,
                  n = 3,
                  labels = c("Low", "Medium", "High"))
employee$sal = as.factor(employee$sal)
```

7. cross-frequency table
```{r}
table(employee$f.age, employee$sal)
```
Salary distribution shows age disparity as the "Young" and "Aged" age groups lack "High" salaries, while the "Medium" group has a more balanced distribution, including "High" salaries.







